UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-03-21 paper/paper.tex
couple of algorithm designs

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{float}

@@

Cost per hour is calculated for each of available pricing schemes. Single result represents a matrix of hours per day and \textit{cph}. Graphical representation of results will produce a graph similar to Figure~\ref{fig:cc2_8xlarge}. Pricing trends are visible. Price drops exponentially for around first 5 hours of usage and almost stabilizes afterwards. Light is the cheapest option for around 15 hours per day usage. This is better visible on Figure~\ref{fig:cph_cc2_8xlarge_zoom}. After 15 hours, it is better to invest in Heavy utilization scheme. This is a point that will be called an intersection point between 2 pricing schemes and referred as \textit{ip(scheme1, scheme2)}. In this example, we can calculate that for cc2.8xlarge instance \textit{ip(light, heavy) = 16}

@@

\subsection{Calculate cost per hour for a given pricing scheme}
\subsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}
\subsection{Collect VM usage data}
\subsection{Group usage metrics by machine}
\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}
\subsection{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}

>>>>

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{float}
\usepackage[]{algorithm2e}

@@

Cost per hour is calculated for each of available pricing schemes. Single result represents a matrix of hours per day and \textit{cph}. Graphical representation of results produces a graph similar to Figure~\ref{fig:cc2_8xlarge}. \par 
This representation allows to notice pricing trends. In the example below, price drops exponentially for around first 5 hours of usage and nearly stabilizes afterwards. Light is the cheapest option for around 15 hours per day usage. This is better visible on Figure~\ref{fig:cph_cc2_8xlarge_zoom}. After 15 hours, it is better to invest in Heavy utilization scheme. This is the point that will be called \textit{an intersection point} between 2 pricing schemes and noted as \textit{ip(scheme1, scheme2)}. \par
For the example below, cc2.8xlarge instance's intersection point between Light and Heavy schemes is \textit{ip(light, heavy) = 16}.

@@

\subsection{Calculate cost per hour for a given pricing scheme}

\begin{algorithm}[H]
 \KwData{Upfront cost, Per hour charge, Utilisation [hours per day];}
 \KwResult{Total cost per hour for a given pricing scheme defined as \textit{cph};}
 read upfront\;
 read perhour\;
 read hours\;	
 return (upfront + (365 * perhour * hours)) / (365 * hours)
 \caption{Calculate cost per hour for a given pricing scheme}
\end{algorithm}

\subsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}

\begin{algorithm}[H]
 \KwData{Array of cph for 2 pricing schemes;}
 \KwResult{Intersection point when one pricing scheme becomes cheaper than the other one;}
 read array1\;
 read array2\;
 \ForAll{cph in array} {
 	\If{$cph2 <= $cph1} {
 		return cph
 	}
 }
\caption{Calculate intersection point between two pricing schemes}
\end{algorithm}

\subsection{Collect VM usage data}

        1,machine ID,INTEGER,YES

        2,start time,INTEGER,YES

        3,end time,INTEGER,YES

        4,duration INTEGER,YES

        5,sampled CPU usage,FLOAT,NO

        6,assigned memory usage,FLOAT,NO

        7,maximum memory usage,FLOAT,NO

\subsection{Group usage metrics by machine}

\begin{algorithm}[H]
 \KwData{VM usage data;}
 \KwResult{Metrics containing calculated duration and day;}
 read vmMetrics\;
 \ForAll{line in vmMetrics} {
        calculateDuration();
        calculateDay();
 }
\caption{VM metrics transformation}

\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}

\subsection{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}
